A 3D curvilinear skeletonization algorithm with application to path tracing

### 2012-12-05 reviews/answer_to_reviewers.tex

\section{Answer to reviewer 2}

\begin{itemize}

\item The discussion in Section 5.2 assumes some things. For example, if there are different sources of light and the image is quite symmetric, it may easily happen that $imp_n=n$. In this case the discussion does not go through.
Also, I get the feeling that the presentation is tailored to ONE light source. It would be better to make clear in the discussion that the method works for several light­sources.

\textit{If there are multiple light sources in the scene, the one closest to $n$ is chosen in order to compute $imp_n$, therefore, we cannot have both points equal. If $n$ is equidistant from two light sources, then (in the current algorithm's version), we choose randomly one light source.
We added the strategy about multiple light sources at the end of section 5.2, just before the "sampling according to L" paragraph.}

@@

\item Why do not define d(x,y) as the $L_1$ ­distance instead of using a graph­based distance?

\textit{We changed the way we introduce, in section 4.2, the distance d, and now rely on the well-known definition of the L1 distance}.\\

\item Why do you call the skeleton curvilinear? What is curvilinear about it?

\textit{The skeleton is called curvilinear because the skeletonization algorithm preserves, in the visual aspect preservation step, only edges. Surfaces may appear if the topology of the object requires it : in this case, these surfaces were not preserved for geometrical reasons, but for topological reasons. Surface skeletons also exist : in this case, surfaces may be preserved during the visual aspect preservation step. Our algorithm is a curvilinear skeletonization algorithm.
We explained this terminology choice in the article, at the end of section 4.3.}\\

### 2012-12-05 application_to_path_tracing.tex
commit or not commit ?

The algorithm computes $L$ as follow: it chooses one random direction $\Phi$ based on the pdf $p$ and applies the estimator by calling $L$ recursively to compute $L_r$ (shoots a new ray in the direction $\Phi$, computes the new hit point with the scene, and compute the new radiance at this point). Finally, it returns the sum of the emitted radiance $L_e$ and the result for $L_r$. The recursion stops when either a maximal number of bounces or a directly illuminated area have been reached.

@@

The skeleton of the voids of the scene is computed using Alg.~\ref{algo::3d_curvskel} (as shown on Fig.~\ref{fig::example_imp} on the right) and is converted to a graph (the nodes are the 0-faces and the edges are the 1-faces). We then compute a set of \myem{importance points}, which will be used to sample $\Omega_x$ in the path tracing algorithm. To each node $n$ of the skeleton, one importance point $imp_n$ is computed. Intuitively, the importance point associated to $n$ is the direction to follow in order to find a light source.

@@

Given a point $x$ on the scene and a direction $\Theta$, we want to compute $L(x \rightarrow \Theta)$ and then sample the hemisphere $\Omega_x$. We search for the nearest skeleton node $n$ to $x$ and its importance point $imp_n$. We sample the hemisphere with a power-cosine pdf centered on $\overrightarrow{x\,imp_n}$:
\begin{center}
$p_{skel}(\Phi) = \frac{s + 1}{2\pi}  * cos^s \alpha$
\end{center}
with $\alpha$ the angle between $\overrightarrow{x\,imp_n}$ and $\Phi$, $s$ being a parameter called skeleton strength. The higher $s$ is, the closer to $\overrightarrow{x\,imp_n}$ we sample.

\subsection{Results and discussion}
Some results are presented on Fig.~\ref{fig:results} and Fig.~\ref{fig::intro_image} where we can see that our method produces less noisy images compared to the regular path tracing. We present, in Fig~\ref{tab:timing}, the time taken by each method to produce an image of same quality (the quality is measured by the mean square error (MSE) with a reference image) in different scenes: our method is the fastest.

>>>>

The algorithm computes $L$ as follow: it chooses one random direction $\Phi$ based on the pdf $p$ and applies the estimator by calling $L$ recursively to compute $L_r$ (shoots a new ray in the direction $\Phi$, computes the new hit point with the scene, and computes the new radiance at this point). Finally, it returns the sum of the emitted radiance $L_e$ and the result for $L_r$. The recursion stops when either a maximal number of bounces or a directly illuminated area have been reached.

@@

The skeleton of the voids of the scene is computed using Alg.~\ref{algo::3d_curvskel} (as shown on Fig.~\ref{fig::example_imp} on the right) and is converted into a graph (the nodes are the 0-faces and the edges are the 1-faces). We then compute a set of \myem{importance points}, which will be used to sample $\Omega_x$ in the path tracing algorithm. To each node $n$ of the skeleton, one importance point $imp_n$ is computed. Intuitively, the importance point associated to $n$ is the direction to follow in order to find a light source.

@@

Given a point $x$ on the scene and a direction $\Theta$, we want to compute $L(x \rightarrow \Theta)$ and then sample the hemisphere $\Omega_x$. We look for the nearest skeleton node $n$ to $x$ and its importance point $imp_n$. We sample the hemisphere with a power-cosine pdf centered on $\overrightarrow{x\,imp_n}$:
\begin{center}
$p_{skel}(\Phi) = \frac{s + 1}{2\pi}  * cos^s \alpha$
\end{center}
with $\alpha$ the angle between $\overrightarrow{x\,imp_n}$ and $\Phi$, $s$ being a parameter called skeleton strength. The higher $s$ is, the closer to $\overrightarrow{x\,imp_n}$ we sample.

\subsection{Results and discussion}
Some results are presented on Fig.~\ref{fig:results} and Fig.~\ref{fig::intro_image} where we can see that our method produces less noisy images compared to the regular path tracing. We present, in Fig~\ref{tab:timing}, the time taken by each method to produce an image of same quality (the quality is measured by the mean square error (MSE) with a reference image) in different scenes: our method is the fastest one.

### 2012-12-05 skeleton_and_pathtracing.tex
commit or not commit ?

\title{A 3D curvilinear skeletonization algorithm with application to path tracing}
\author{John Chaussard\inst{1} \and Laurent No\"{e}l\inst{2} \and Venceslas Biri\inst{2} \and Michel Couprie\inst{2}\thanks{This work has been partially supported by the \quotes{ANR-2010-BLAN-0205 KIDICO} project}}
\institute{Universit\'{e} Paris 13, Sorbonne Paris Cit\'{e}, LAGA, CNRS(UMR 7539), \\ F-93430, Villetaneuse, France \\ \email{chaussard@math.univ-paris13.fr}
\and
Universit\'{e} Paris Est, LIGM, A3SI-ESIEE \\ 2, boulevard Blaise Pascal, 93162 Noisy le Grand CEDEX, France \\ \email{laurent.noel@esiee.fr, v.biri@esiee.fr, michel.couprie@esiee.fr}}

>>>>

\title{A 3D curvilinear skeletonization algorithm with application to path tracing}
\author{John Chaussard\inst{1} \and Laurent No\"{e}l\inst{2} \and Venceslas Biri\inst{2} \and Michel Couprie\inst{2}\thanks{This work has been partially supported by the \quotes{ANR-2010-BLAN-0205 KIDICO} project}}
\institute{Universit\'{e} Paris 13, Sorbonne Paris Cit\'{e}, LAGA, CNRS(UMR 7539), \\ F-93430, Villetaneuse, France \\ \email{chaussard@math.univ-paris13.fr}
\and
Universit\'{e} Paris Est, LIGM, A3SI-ESIEE, CNRS(UMR 8049) \\ 2, boulevard Blaise Pascal, 93162 Noisy le Grand CEDEX, France \\ \email{laurent.noel@esiee.fr, v.biri@esiee.fr, michel.couprie@esiee.fr}}
